---
title: "講義1課後作業：編輯`effectsize` 套件使用指南"
author: "協同編輯"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = FALSE
)

if(!require(effectsize)){install.packages("effectisize");library(effectsize)}else{library(effectsize)}
```




經過[第一堂課程](Lecture01.html)，為了各位學員之後在各種場域教授與討論效果量的計算與解讀，有一套可示範的R程式碼及說明範例是相當有用的。我們將彙整Ben-Shachar等人(2020)開發的[R套件`effect size`](https://easystats.github.io/effectsize/index.html)，與Ellis(2010)Chapter 1,2的內容，以接力協作的方式編輯這份作業。每位學員貢獻一點成果，換取更多人在研究教學上的便利。


> 編輯建議：1. 使用純文字與[Latex編碼](http://tug.ctan.org/info/latex-refsheet/LaTeX_RefSheet.pdf)編輯效果量公式及範例說明; 2. 在R chunk內放置可執行的R程式碼; 3. 隨時按'Knit'渲染可得編輯成果; 4. 編輯完成請在[討論區](https://github.com/Rstat-project/seed_courses/discussions)留言提交作業成果。


## 計算效果量

### d family ~ difference between groups

#### Groups compared on dichotomous outcomes


- The risk difference in probabilities

- The relative risk

- The odds ratio

#### Groups compared on continuous outcomes

- Cohen’s d

比較獨立樣本平均數的效果量Cohen's d計算公式
$$Cohen's \space d = \frac{M_1 - M_2}{SD_{pooled}} $$

```{r echo=TRUE}
## 獨立樣本比較範例
cohens_d(mpg ~ am, data=mtcars)
## 輸出效果量及95%信賴區間
```


- Glass’s delta( $\triangle$ )

- Hedges’ g 

- Probability of superiority


### r family ~ measures of association


#### Correlation indexes

(Two variables are continuous)

- The Pearson product moment correlation coefﬁcient ($r$) 


(Two variables are ordinal)

- Spearman’s rho or the rank correlation coefﬁcient ($\rho$)

- Kendall’s tau ($\tau$)

(One continous and one ordinal)

- The point-biserial correlation coefﬁcient ($r_{pb}$)

(Contigency table)

- The phi coefﬁcient ($\phi$)

- Pearson’s contingency coefﬁcient (C)

- Cram´er’s V (V)

- Goodman and Kruskal’s lambda ($\lambda$)


#### Proportion of variance indexes

- The coefﬁcient of determination ($r^2$)


- the (uncorrected) coefﬁcient of multiple determination ($R^2$$)


- the coefﬁcient of multiple determination adjusted for sample size and the number of predictor variables ($_{adj}R^2$$)


- Cohen’s f ($f$)


- Cohen’s f squared


- Epsilon squared ($eps^2$)


- the (uncorrected) correlation ratio ($\eta^2$)


- Omega squared ($\omega^2$)


- The squared canonical correlation coefﬁcient ($R^2_C$)

## 解讀效果量

> `effectsize`套件收錄統計學者的建議，提供使用者查詢預估效果量的**份量**。




#### 參考資源

Ben-Shachar, M. S., Lüdecke, D., & Makowski, D. (2020). effectsize: Estimation of effect size indices and standardized parameters. Journal of Open Source Software, 5(56), 2815. https://doi.org/10.21105/joss.02815
