---
title: "Lecture02_HW.Rmd"
author: "my name"
date: "2022/5/4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

if(!require(effectsize)){install.packages("effectsize")}

if(!require(pwr)){install.packages("pwr")}
```




## pwr實作演練

- 題目改編自[PsyteachR: Analysis 8.3](https://psyteachr.github.io/analysis-v2/apes---alpha-power-effect-sizes-sample-size.html#practical-apes-calculations)

**Cohen's d的建議大小**

```{r d_table, echo=FALSE}
d <- seq(from=.1,to=.9,by=.1)
effect_size <- effectsize::interpret_cohens_d(seq(from=.1,to=.9,by=.1))

bench <- data.frame(
  effect_size,
  d
)
```

`r knitr::kable(bench)`

單一樣本t檢定/相依樣本t檢定的Cohen's d

$$d = \frac{t}{sqrt(N)}$$

獨立樣本t檢定的Cohen's d

$$d = \frac{2t}{sqrt(df)}$$


### Task 1: Effect size from a one-sample t-test

剛才完成一項單一樣本t檢定，報告結果 _t_(23) = 2.35, _p_ = .002。請寫出能回答以下問題的R code：

- 計算效果量到小數點後二位：
- 根據Cohen(1988)的建議，這是一個___效果量。


### Task 2: Effect size from a two-sample t-test

剛才完成一項獨立樣本t檢定，報告結果 _t_(34) = 3.2, _p_ = .001。請寫出能回答以下問題的R code：

- 計算效果量到小數點後二位：
- 根據Cohen(1988)的建議，這是一個___效果量。

### Task 3: Effect size from a one-sample t-test

剛才完成一項相依樣本t檢定，報告結果 _t_(40) = 2.8, _p_ = .005。請寫出能回答以下問題的R code：

- 計算效果量到小數點後二位：
- 根據Cohen(1988)的建議，這是一個___效果量。

### Task 4: t-value and effect size for a between-subjects experiment



### Task 5: Sample size for standard power one-sample t-test



### Task 6: Effect size from a high power between-subjects t-test



### Task 7: Power of Published Research


